\newpage
\begin{english}
\begin{center}
\textbf{FreeBSD Documentation License}
\end{center}
Copyright 2006, Arabeyes.org. All rights reserved.

Redistribution and use in source (SGML DocBook) and 'compiled' forms (SGML, HTML, PDF, PostScript, RTF and so forth) with or without modification, are permit
ted provided that the following conditions are met:

Redistributions of source code (SGML DocBook) must retain the above copyright notice, this list of conditions and the following disclaimer as the first lines
 of this file unmodified.

Redistributions in compiled form (transformed to other DTDs, converted to PDF, PostScript, RTF and other formats) must reproduce the above copyright notice, 
this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.

Important: THIS DOCUMENTATION IS PROVIDED BY THE ARABEYES WIKI TEAM "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
 WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE ARABEYES WIKI TEAM BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, 
OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR 
OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS DOCUMENTATION, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
\vspace{1 cm}

Document generation: Abderrahim Kitouni, \url{a.kitouni@gmail.com}
\end{english}

\newpage
\begin{Arabic}
\begin{center}
\textbf{رخصة فري‌بي‌إس‌دي للوثائق}
\end{center}

حقوق النسخ 2006، \textenglish{Arabeyes.org}. كل الحقوق محفوظة.

يُسمح بإعادة التوزيع والاستخدام بعد التعديل أو بدونه في هيئة المصدر \textenglish{(SGML DocBook)} أو الهيئات "المجمعة" (\textenglish{SGML} أو \textenglish{HTML} أو \textenglish{PDF} أو \textenglish{PostScript} أو \textenglish{RTF}... إلخ) بالشروط الآتية:

يجب أن يتم الاحتفاظ بسطر حقوق النسخ المذكور أعلاه وقائمة الشروط هذه وإخلاء الطرف المذكور أدناه بدون تغيير عند إعادة التوزيع في هيئة الشفرة المصدرية \textenglish{(SGML DocBook)}.

يجب أن يتم توليد سطر حقوق النسخ المذكور أعلاه، وقائمة الشروط هذه، وإخلاء الطرف المذكور أدناه، وأن يظهروا في التوثيق و/أو أي مواد أخرى يتم توفيرها في المجموعة عند إعادة التوزيع في الهيئة المجمعة (محولة إلى نوع آخر من \textenglish{DTD}، محولة إلى \textenglish{PDF} أو \textenglish{PostScript} أو \textenglish{RTF} أو أي هيئة أخرى).

هام: يتم توفير مستند التوثيق هذا بواسطة فريق ويكي عرب آيز "كما هو" مع إخلاء الطرف من أي ضمانات صريحة أو مُبْطَنة، بما فيها أي ضمانات مناسبة المنتج للتجارة أو لياقته لأي هدف. لا يمكن تحميل فريق ويكي عرب آيز أي مسئولية عن أي تعويض، مباشر أو غير مباشر أو غير مقصود أو خاص أو عقابي أو تبعي (بما فيها اقتناء سلع أو خدمات بديلة؛ خسارة بيانات أو أرباح أو حق استخدام؛ أو تدخل في عمل) مهما كانت النظرية التي تم تأسيس علاقة السببية عليها سواء كانت مسئولية عقدية أو لازمة أو مدنية (متضمنة الإهمال أو غير ذلك)، والتي تطرأ بأي شكل عن استخدام هذا التوثيق، حتى لو تم التحذير من وقوع مثل هذا الضرر.
\vspace{1cm}

توليد الملف : عبد الرحيم قيطوني \url{a.kitouni@gmail.com}
\end{Arabic}

\end{document}
